### 2020-03-03 doc/icfp20/counterpoint.tex
prepare code for submission

motionCheck : PitchInterval \(\rightarrow\) PitchInterval \(\rightarrow\) Maybe MotionError
motionCheck i1 i2 with motion i1 i2 | isPerfect (proj\(\sb{\mathtt{2}}\) i2)
motionCheck i1 i2 | contrary | \_     = nothing
motionCheck i1 i2 | oblique  | \_     = nothing
motionCheck i1 i2 | parallel | false = nothing
motionCheck i1 i2 | parallel | true  = just (parallel i1 i2)
motionCheck i1 i2 | similar  | false = nothing
motionCheck i1 i2 | similar  | true  = just (similar i1 i2)

@@

\begin{alltt}
fs : FirstSpecies
fs = firstSpecies first1 middle1 last1 refl refl refl refl
\end{alltt}

@@

\noindent In \citet{cong-cp}'s implementation, on the other hand,
the invalid motion results in an unsolved metavariable \texttt{\_13},
representing the proof that the two intervals form a valid motion:

@@

\noindent Compared to the error message produced by our
implementation, this lacks the exact information about the motion
between the two intervals.

We would also like to note that the attempt to precisely reporting
musical errors has appeared in the work by \citet{szamozvancev-welltyped}.
They formalize various musical rules, including those for intervals
and motion, using GHC's custom type error feature.
However, they do not aim to fully support species counterpoint,
and thus do not cover as many rules as we do.

>>>>

motionCheck : PitchInterval \(\rightarrow\) PitchInterval \(\rightarrow\) Maybe MotionError
motionCheck i1 i2 with motion i1 i2 | isPerfect (proj\(\sb{2}\) i2)
motionCheck i1 i2 | contrary | \_     = nothing
motionCheck i1 i2 | oblique  | \_     = nothing
motionCheck i1 i2 | parallel | false = nothing
motionCheck i1 i2 | parallel | true  = just (parallel i1 i2)
motionCheck i1 i2 | similar  | false = nothing
motionCheck i1 i2 | similar  | true  = just (similar i1 i2)

@@

\begin{alltt}
fs : FirstSpecies
fs = firstSpecies first middle last refl refl refl refl
\end{alltt}

@@

\noindent In \citet{cong-cp}'s implementation, on the other hand,
the invalid motion results in an unsolved metavariable \texttt{\_13},
meaning that Agda failed to construct a proof required by the
counterpoint constructor:

@@

\noindent For a non-expert user, it may be difficult to connect
this message to the corresponding musical error \footnote{
  The attempt to produce customized musical errors has also
  appeared in \citet{szamozvancev-welltyped}.
  They formalize various musical rules, including those for
  intervals and motion, using GHC's custom type error feature.
  However, their error messages are not as precise as ours:
  e.g., for the parallel octave example, they simply report
  ``\texttt{Direct motion into a perfect octave is forbidden}'',
  without the precise information about the two intervals and
  the motion between them.}.
